### 2023-03-17 main.tex
E comment

 \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$. However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, we can write the Hadamard formula as 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
For the following of the proof we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
    \item for $A=E_{\ell 1}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{\ell 1}\exp{(E)}=E_{\ell 1}
    because $E_{\ell 1}$ commutes with $E$
    \item for $A=E_{\ell\ell}$ with $\ell \in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{\ell \ell}\exp{(E)}=E_{\ell \ell}+E_{\ell 1}
Indeed, using \eqref{eq:comgl} we have 
       \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{1\ell}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{1 \ell}\exp{(E)}=E_{1\ell}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{j\ell}\right)
    Indeed, using \eqref{eq:comgl} we have 
[E,E_{1\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{11}-E_{11}\delta_{a\ell}\right)=\sum_{j=2}^{N}E_{j\ell}-E_{11};
\left[E,[E,E_{1\ell}]\right]&=\sum_{b=2}^{N}\sum_{j=2}^{N}\left[E_{b1},E_{j\ell}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
\sum_{j,b=2}^{N}\left(E_{b\ell}\delta_{j1}-E_{j1}\delta_{b\ell}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
-2\sum_{j=2}^{N}E_{j1};
Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
\item for $A=E_{k\ell}$ with $k,\ell \in \{2,\ldots,N\}$ we obtain 
\begin{equation}\label{HT-Ekl}
    \exp{(-E)}E_{\ell k}\exp{(E)}=E_{k\ell}+E_{\ell 1}
   Indeed, using \eqref{eq:comgl} we have 
[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{\ell 1}-E_{\ell 1}^{x}\delta_{ak}\right)=-E_{\ell 1}^{x};
Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-Ekl}.
\item for $A=E_{11}$ we obtain 
\begin{equation}\label{HT-E11}
    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{j=2}^{N}E_{j1}^{x}
  Indeed, using \eqref{eq:comgl} we have

>>>>

 \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 {\color{blue} That's confusing. What is E?}

 However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, we can write the Hadamard formula as 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
For the following of the proof we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
\begin{enumerate}
    \item for $A=E_{\ell 1}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{\ell 1}\exp{(E)}=E_{\ell 1}
    \end{equation}
    because $E_{\ell 1}$ commutes with $E$
    \item for $A=E_{\ell\ell}$ with $\ell \in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{\ell \ell}\exp{(E)}=E_{\ell \ell}+E_{\ell 1}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation*}
       \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
    \end{equation*}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{1\ell}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{1 \ell}\exp{(E)}=E_{1\ell}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{j\ell}\right)
    \end{equation}
    Indeed, using \eqref{eq:comgl} we have 
    \begin{equation*}
[E,E_{1\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{11}-E_{11}\delta_{a\ell}\right)=\sum_{j=2}^{N}E_{j\ell}-E_{11};
\end{equation*}
and 
\begin{equation*}
\begin{split}
\left[E,[E,E_{1\ell}]\right]&=\sum_{b=2}^{N}\sum_{j=2}^{N}\left[E_{b1},E_{j\ell}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
\\&=
\sum_{j,b=2}^{N}\left(E_{b\ell}\delta_{j1}-E_{j1}\delta_{b\ell}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
\\=&
-2\sum_{j=2}^{N}E_{j1};
\end{split}
\end{equation*}
Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
\item for $A=E_{k\ell}$ with $k,\ell \in \{2,\ldots,N\}$ we obtain 
\begin{equation}\label{HT-Ekl}
    \exp{(-E)}E_{\ell k}\exp{(E)}=E_{k\ell}+E_{\ell 1}
\end{equation}
   Indeed, using \eqref{eq:comgl} we have 
\begin{equation*}
[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{\ell 1}-E_{\ell 1}^{x}\delta_{ak}\right)=-E_{\ell 1}^{x};
\end{equation*}
Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-Ekl}.
\item for $A=E_{11}$ we obtain 
\begin{equation}\label{HT-E11}
    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{j=2}^{N}E_{j1}^{x}
\end{equation}
  Indeed, using \eqref{eq:comgl} we have
